Challenges and Solutions of Developing and Implementing a Novel Desktop-as-a-Service

### 2024-04-29 paper.tex
Minor Language improvemens

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.21 of 2022/01/12
%
\documentclass[runningheads]{llncs}
%
\usepackage[T1]{fontenc}
% T1 fonts will be used to generate the final print and online PDFs,
% so please use T1 fonts in your manuscript whenever possible.
% Other font encondings may result in incorrect characters.
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following two lines
% to display URLs in blue roman font according to Springer's eBook style:
%\usepackage{color}
%\renewcommand\UrlFont{\color{blue}\rmfamily}
%\urlstyle{rm}
%
\begin{document}
%
\title{Challenges and Solutions of Developing and
	Implementing a Revolutionary Novel Desktop-as-a-Service}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Christian Baun \and 
Johannes Bouché}
% \author{Christian Baun\orcidID{0009-0004-9955-3752} \and
% 	Johannes Bouché\orcidID{TODO}}
%
\authorrunning{C. Baun, J. Bouché}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Faculty of Computer Science and Engineering,\\
Frankfurt University of Applied Sciences,\\
Nibelungenplatz 1, 60318 Frankfurt am Main, Germany
\email{[christianbaun|johannes.bouche]@fb2.fra-uas.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Desktop-as-a-Service (DaaS) is a cloud service category with great potential for improving the everyday work of running and using applications. However, existing DaaS solutions have several drawbacks, which have limited the popularity of this service category in the past. Our novel DaaS solution called DESIGN not only overcomes the limitations of existing solutions but also offers significant benefits. It has the potential to revolutionize the way we use applications, supporting non-modified Linux and Windows applications with just a browser on the client side. This paper describes some of the knowledge we gained during the development because of the challenges we faced and the solutions we found.

@@

\begin{table}
	\centering
	\caption{Services used by our DaaS for Remote Access to individual Linux or Windows Applications}
	\begin{tabular}{|l|c|c|c|c|}
		\hline
		\textbf{Service}    &  \textbf{Protocol}  & \textbf{Single Window}       & \textbf{Operating} & \textbf{Software}  \\
		\textbf{implementation}  &                & \textbf{Mode}                & \textbf{System}    & \textbf{License}   \\
		\hline
		TightVNC            &  VNC                & supported                    & Windows            & GPL2               \\
		\hline
		Windows RDP server  &  RDP                & supported                    & Windows            & proprietary        \\
		\hline
		x11vnc              &  VNC                & supported                    & Linux              & GPL2               \\
		\hline
		Xrdp                &  RDP                & supported                    & Linux              & Apache 2.0         \\
		\hline
	\end{tabular}
	\label{tab:DaaS_Services_Overview}
\end{table}

>>>>

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.21 of 2022/01/12
%
\documentclass[runningheads]{llncs}
%
\usepackage[T1]{fontenc}
% T1 fonts will be used to generate the final print and online PDFs,
% so please use T1 fonts in your manuscript whenever possible.
% Other font encondings may result in incorrect characters.
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following two lines
% to display URLs in blue roman font according to Springer's eBook style:
%\usepackage{color}
%\renewcommand\UrlFont{\color{blue}\rmfamily}
%\urlstyle{rm}
%
\begin{document}
%
\title{Challenges and Solutions of Developing and
	Implementing a Novel Desktop-as-a-Service}
%
\titlerunning{Challenges and Solutions of Developing and
	Implementing a Novel DaaS}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Christian Baun \and 
Johannes Bouché}
% \author{Christian Baun\orcidID{0009-0004-9955-3752} \and
% 	Johannes Bouché\orcidID{TODO}}
%
\authorrunning{C. Baun, J. Bouché}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Faculty of Computer Science and Engineering,\\
Frankfurt University of Applied Sciences,\\
Nibelungenplatz 1, 60318 Frankfurt am Main, Germany
\email{[christianbaun|johannes.bouche]@fb2.fra-uas.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Desktop-as-a-Service (DaaS) is a cloud service category with a tremendous potential for improving the everyday work of running and using applications. However, existing DaaS solutions have several drawbacks, which have limited the popularity of this service category in the past. Our novel DaaS solution called DESIGN not only overcomes the limitations of existing solutions but also offers significant benefits. It has the potential to revolutionize the way we use applications, supporting non-modified Linux and Windows applications with just a browser on the client side. This paper describes some of the knowledge we gained during the development because of the challenges we faced and the solutions we found.

@@

\begin{table}
	\centering
	\caption{Services used by our DaaS for Remote Access to individual Applications}
	\begin{tabular}{|l|c|c|c|c|}
		\hline
		\textbf{Service}    &  \textbf{Protocol}  & \textbf{Single Window}       & \textbf{Operating} & \textbf{Software}  \\
		\textbf{implementation}  &                & \textbf{Mode}                & \textbf{System}    & \textbf{License}   \\
		\hline
		TightVNC            &  VNC                & supported                    & Windows            & GPL2               \\
		\hline
		Windows RDP server  &  RDP                & supported                    & Windows            & proprietary        \\
		\hline
		x11vnc              &  VNC                & supported                    & Linux              & GPL2               \\
		\hline
		Xrdp                &  RDP                & supported                    & Linux              & Apache 2.0         \\
		\hline
	\end{tabular}
	\label{tab:DaaS_Services_Overview}
\end{table}
